Marginalization of photometric redshift uncertainties

### 2020-07-17 Paper/paper.tex
Updates from Overleaf

        We assume that the cosmic covariance between the tomographic bins is negligible, so we estimate the cosmic variance covariance matrix by treating each bin independently. We show the resulting correlation matrix of the COSMOS cosmic variance in Fig. \ref{fig:CV}.

@@

\subsection{The HSC dataset}
The Hyper-Suprime Cam survey is an on-going photometric galaxy survey survey focused mainly on weak gravitational lensing. The analysis in Ref.~\cite{1912.08209} is based on the publicly-available HSC DR1 data, whose so-called wide fields cover approximately 108 square degrees on the sky, subdivided into seven distinct patches. Ref.~\cite{1912.08209} used these data to compute spherical harmonic galaxy clustering power spectra for four tomographic redshift bins between $z=0.15$ and $z=1.5$, taking both auto- and cross-correlations into account. These power spectra have been corrected for observational and extragalactic systematics by deprojection at the map-level \cite{2019MNRAS.484.4127A}. Finally, following Ref.~\cite{2019PASJ...71...43H}, photometric redshift distributions have been estimated by cross-matching HSC galaxies to galaxies in the COSMOS 30-band photometric catalog presented in Ref.~\cite{2016ApJS..224...24L}.
\subsection{Validating the linear expansion}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Tmat}
\caption{Visualization of the derivative matrix $T_{mn} = {\partial t_m}/{\partial N_n}$. \todo{Make look nicer: split into tomo bins}} 
\label{fig:Tmat}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Nzs}
\caption{Photometric redshift
distributions $N(z)$
of the four tomographic HSC bins.
The \textit{red} curves show the
default values used in the 
full HSC analysis (CITE Andrina),
while the \textit{blue} curves 
show their smoothed and upsampled 
version used in this work. The
\textit{green} show a random 
Gaussian draw from the smoothing 
prior described in Section TODO: Section}
\label{fig:Nzs}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Cls}
\caption{Galaxy power spectrum, $C_\ell^{gg}$, between the four
tomographic bins. The \textit{black} curves show the HSC-measured
power spectrum and error bars, while the
\textit{red} curves present the $C_\ell$s
computed using the posterior mean values of the 6 HOD parameters from the
full HSC analysis (CITE Andrina). In 
\textit{green} is shown the power
spectrum obtained by using the smoothed
$N(z)$ distributions (see Fig. \ref{fig:Nzs}). The \textit{blue}
curves correspond to the exact
calculation of the $C_\ell$s using the
perturbed $N(z)$ values in
Fig. \ref{fig:Nzs}, and the 
\textit{lightblue} dotted lines
show the power spectra derived via
Taylor expansion: $C_\ell' = C_\ell +
 {\sf T} \left(\vN' - {\vN} \right)$.}
\label{fig:Cls}
\end{figure}

@@

 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:lin}
\caption{$\chi^2$ values with respect to the HSC data of the four curves shown in Fig. \ref{fig:Cls}. $[\mu_1, \ \mu_{1,p}] =  [13.05, 0.79]$
Ratio of determinants of original precision to CV+noise+smooth precision per dof =  1.15
94}
\end{table}

Fig. \ref{fig:Nzs} shows the distribution of the
photometric redshifts of the HSC data

Fig. \ref{fig:Cls} displays the exact $C_\ell$ vs. 
linear prediction using the derivative matrix, ${\sf T}$.

In Fig. \ref{fig:Tmat}, we show the
derivative matrix, ${\sf T}$,
defined in Eq. \ref{eq:Tmat} for the first tomographic
bin in the HSC data and its cross-correlations with
all four bins, i.e. . The rows of the matrix correspond
to the $\ell$ multipoles, while the columns to the
redshift samples of $N(z)^1$.

\subsection{Impact of N(z) uncertainties on final parameters}
To study the effect on the covariance matrix
of the marginalization procedure described in detail
in sections TODO: CITE, we visualize the original
correlation matrix and its difference with the
marginalized matrix in Fig. \ref{fig:fid_marg_cov}. The
main effects on the original matrix is
a positive contribution to the off-diagonal entries
for redshift samples in close proximity. We set the free
parameters of our model to the following values: 
$A_{\rm smooth} = 1$, $A_{\rm noise} = 4.$,
$N_{\rm upsample} = 3$, and $\Delta z_{\rm thresh} = 
0.06$. These values were chosen so as to reduce the
$\chi^2$ of the perturbed model 
using the new covariance matrix when compared with the
original covariance matrix. The modest value of the
smoothing parameter, $A_{\rm smooth}$, ensure that we 
are not oversmoothing the $N(z)$ distribution, while
the choice of photometric noise as four times 
larger than the variance in the different photometric
measures provides a reasonable guess for the expected
variation in $N(z)$ given the uncertainty.

To assess whether the marginalization procedure 
proposed in this work provides better constraints
on the
6 HOD parameters than the original 14-parameter
model, we employ the ensemble sampler for Markov
chain Monte Carlo (MCMC) $\textsc{emcee}$ CITE Goodman 
\& Weare (2010) and other paper with 6 parameters and
a walkers' ratio of 6 for 12000 iterations. We assess
the convergence of the chains with a simple G-R test
having computed the auto-correlation and thinned the
chains beforehand. In all cases, we find that the
chains are reasonably well converged.

In Fig. \ref{fig:fid_marg_cov}, we show the key 
comparison between

We can
see that the full analysis leads to 
worse constraints on the parameters
when compared with the marginalized
covariance. Furthermore, the proximity
of the \textit{blue} and \textit{red} 
contours serves both as a sanity check 
that our method yields physical constraints
of the 6 parameters (i.e. not exceeding
the cosmic variance limits) as well as 
nearly optimal such

We, furthermore, run the following several 
tests to check the robustness of our result:
\begin{itemize}
\item We study the effect of the smoothing
by turning it off, $A_{\rm smooth} = 0$. 
\item We vary the choice for the
diagonal photometric noise parameter
by increasing it to $A_{\rm noise} = 42$.
\item We compute the ${\sf T}$ matrix 
using a different set of 
HOD parameters perturbed by $1\sigma$
away from the fiducial ones.
\end{itemize}
We show these comparisons with the
fiducial marginalized $N(z)$ model in Fig.
\ref{fig:triangle_marg_tests}.
One can notice that the effect of the
smoothing on the constraints is minimal,
while increasing the diagonal noise
leads to weakening them. Neither of these
tests changes significantly the
mean of the posterior distribution.
On the other hand, offsetting the 
HOD parameters used in the ${\sf T}$
matrix computation leads to a shift to
the mean and a slight widening of the
contours. That is because the covariance
matrix used in the analysis no longer
favors the HOD values preferred by the
data. This slight tension
results in sub-par convergence
of the chains and shifted mean posteriors.

\ref{fig:triangle_fid_marg}
\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_diff}
\end{subfigure}
\caption{Correlation matrix of the original HSC dataset (\textit{left} panel) and difference between the
original and the marginalized (this work)
correlation matrices (\textit{right} panel). Most of the
effect of marginalizing for the shift and width
parameters is manifested as a positive contribution
to the original matrix near the diagonal (i.e. there
is an increase in correlation for close redshift
values). Note that we have subtracted the diagonal
off the two matrices.}
\label{fig:fid_marg_cov}
\end{figure}

@@

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_marg_tests}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using different choices for the marginalized covariance matrix: in \textit{green}, we show the result where the diagonal noise is set to a very large value ($A_{\rm noise} = 42$); in \textit{gray} is shown the case where the marginalization is performed assuming fiducial HOD-model values which are $1\sigma$ away from their posterior mean values taken from \todo{CITE Andrina's paper}; in \textit{red}, we display the case where the smoothing has been removed ($A_{\rm smooth} = 0$); and finally the \textit{blue} contours show the fiducial case with $A_{\rm noise} = 4$ and $A_{\rm smooth} = 1$.}
\label{fig:triangle_marg_tests}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & HSC cov. [68\%, 95\%] & CV constraints [68\%, 95\%] & Marg. $N(z)$ [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 87.49/80 & --- & 88.54/88 \\ 
$\mu_{{\rm min},p}$ & $-0.5^{+1.7}_{-2.0}$, $^{+4.0}_{-4.0}$ & $-0.4^{+1.1}_{-1.4}$, $^{+2.5}_{-2.3}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ \\ [1ex]
$\mu_{\rm min}$ & $11.90^{+0.26}_{-0.15}$, $^{+0.39}_{-0.46}$ & $11.86^{+0.19}_{-0.16}$, $^{+0.28}_{-0.30}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ \\ [1ex]
$\mu_{0,p}$ & $2.4\pm 4.3$, $^{+7.2}_{-7.0}$ & $2.1^{+4.2}_{-5.1}$, $^{+6.6}_{-7.2}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.7\pm 3.3$, $^{+5.5}_{-5.5}$ & $6.1^{+4.6}_{-3.8}$, $^{+5.2}_{-4.8}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ \\ [1ex]
$\mu_{1,p}$ & $0.9^{+2.0}_{-2.8}$, $^{+5.1}_{-4.7}$ & $0.9^{+1.3}_{-1.8}$, $^{+3.4}_{-2.9}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ \\ [1ex]
$\mu_{1}$ & $13.10^{+0.30}_{-0.21}$, $^{+0.48}_{-0.54}$ & $13.04\pm 0.21$, $^{+0.38}_{-0.40}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:chi2_tests}
\caption{Table showing the minimum
$\chi^2$ value as well as the 68\% and 95\% constraints on the 6 HOD parameters
in three regimes: using the original
HSC covariance matrix with 14 parameters (6 HOD + 8 $N(z)$ ones),
importance-sampling the original
chain to get cosmic variance constraints on the parameters, and finally using the
marginalized $N(z)$ covariance matrix with the 6 HOD parameters developed in this work.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & Fiducial [68\%, 95\%] & Test 1 [68\%, 95\%] & Test 2 [68\%, 95\%] & Test 3 [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 88.54/88 & 87.67/88 & 88.56/88 & 78.61/88 \\ 
$\mu_{{\rm min},p}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ & $0.0\pm 1.7$, $^{+3.2}_{-3.3}$ & $-0.3^{+1.4}_{-1.8}$, $^{+3.2}_{-2.8}$ & $-0.8^{+1.8}_{-2.1}$, $^{+3.7}_{-3.5}$ \\ [1ex]
$\mu_{\rm min}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ & $11.85^{+0.22}_{-0.13}$, $^{+0.31}_{-0.37}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.33}_{-0.36}$ & $11.76^{+0.26}_{-0.17}$, $^{+0.38}_{-0.43}$ \\ [1ex]
$\mu_{0,p}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.8^{+3.6}_{-5.2}$, $^{+5.6}_{-5.5}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.9\pm 3.4$, $^{+5.5}_{-5.6}$ \\ [1ex]
$\mu_{1,p}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ & $1.5^{+2.1}_{-2.6}$, $^{+4.3}_{-3.9}$ & $0.98^{+1.5}_{-2.5}$, $^{+4.2}_{-3.5}$ & $0.6^{+1.9}_{-2.9}$, $^{+4.6}_{-4.0}$ \\ [1ex]
$\mu_{1}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ & $13.03^{+0.26}_{-0.20}$, $^{+0.41}_{-0.45}$ & $13.00^{+0.25}_{-0.22}$, $^{+0.42}_{-0.44}$ & $12.93^{+0.29}_{-0.24}$, $^{+0.47}_{-0.50}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\label{tab:chi2_tests}
\caption{Table}
\end{table}

>>>>

        We assume that the cosmic covariance between the tomographic bins is negligible, so we estimate the cosmic variance covariance matrix by treating each bin independently. We show the resulting correlation matrix of the COSMOS cosmic variance in Fig.~\ref{fig:CV}.

@@

\subsection{The HSC dataset}
The Hyper-Suprime Cam survey is an on-going photometric galaxy survey survey focused mainly on weak gravitational lensing. The analysis in Ref.~\cite{1912.08209} is based on the publicly-available HSC DR1 data, whose so-called wide fields cover approximately 108 square degrees on the sky, subdivided into seven distinct patches. Ref.~\cite{1912.08209} used these data to compute spherical harmonic galaxy clustering power spectra for four tomographic redshift bins between $z=0.15$ and $z=1.5$, taking both auto- and cross-correlations into account. These power spectra have been corrected for observational and extragalactic systematics by deprojection at the map-level \cite{2019MNRAS.484.4127A}. Finally, following Ref.~\cite{2019PASJ...71...43H}, photometric redshift distributions have been estimated by cross-matching HSC galaxies to galaxies in the COSMOS 30-band photometric catalog presented in Ref.~\cite{2016ApJS..224...24L}.

\subsection{Validating the linear expansion}\label{ssec:hsc.lin}
In this section, we study how the linear
approximation performed via the derivative 
matrix ${\sf T}$ (defined in Eq. \ref{eq:Tmat})
compares with the exact calculation. The
derivative matrix can be seen in Fig.~\ref{fig:Tmat}
for the first tomographic
bin and its cross-correlations with
all four bins in the HSC data, 
i.e. the tomographic pairs [1,1], [1,2],
[1,3], and [1,4]. The rows of the matrix correspond
to the $\ell$ multipoles available for each pair, 
while the columns to the 300 equally
spaced redshift samples of $N(z)$
between $z = 0$ and $z = 4$. We can notice that
as we move to pairs with bins at higher redshifts,
the peak of the matrix appears at different locations:
namely, the high-$\ell$ high-$z$ regions of the matrix.
In the $z$ direction, these coincide with the maxima
of the photometric redshifts of the HSC data, shown in
Fig.~\ref{fig:Nzs}. Furthermore, we illustrate the
effect of the smoothing prior (see 
Section~\ref{sssec:theory.prior.smooth})
on the $N(z)$ distributions as well as a perturbed $N(z)$
set, obtained by adding the noise as
a Gaussian random draw from the new marginalized $N(z)$ covariance matrix to the smoothed $N(z)$'s.
The corresponding angular power spectra, $C_\ell$,
for the three cases are shown in Fig.~\ref{fig:Cls}
in their respective colors. Furthermore, 
Fig.~\ref{fig:Cls} illustrates the comparison
between the exact $C_\ell$'s (\textit{yellow line}) with 
the linear prediction using the derivative matrix, ${\sf T}$,
(\textit{dotted light-blue line}). We find that the
two are in reasonably good agreement provided the current 
dataset degree of precision. See Appendix B \todo{to be done} 
for a short explanation of
why the auto-correlation cannot be well-approximated
using linear expansion. The $\chi^2$ values for all four
curves with respect to the HSC data are shown in Table~
\ref{tab:lin}. Comparing the $\chi^2$ 
values for the original and smoothed $N(z)$ distributions,
we notice that they decrease for both the
HSC covariance matrix and also for the marginalized one.
As expected, perturbing the photometric distributions
gets penalized, but the change in the $\chi^2$ value
is much larger for the original HSC covariance, which
indicates that the marginalized covariance is more lenient in
allowing small (and expected) $N(z)$ fluctuations.
The difference between the last two lines suggests 
that the Taylor expansion works sufficiently well,
as the difference in $\chi^2$ is negligible. Finally,
comparing the $\chi^2$ for the new
and old covariances, we are led to conclude that the
new covariance provides a better fit to the data.
We note that we have fixed the values of
all the shift and width parameter to be zero and set the
6 HOD parameters to their \textbf{fiducial}
values of:
\begin{itemize}
    \item $\mu_{\rm min} = 11.88$, $\mu_{\rm min,p} = -0.5$,
    \item $\mu_{\rm 0} = 5.7$, $\mu_{\rm 0,p} = 2.5$,
    \item $\mu_{\rm 1} = 13.08$, $\mu_{\rm 1,p} = 0.9$.
\end{itemize}
These HOD values
are selected to match the 6 posterior means reported in Ref.
\cite{1912.08209}. For the smoothed and perturbed
$N(z)$ values only, we minimize the likelihood to find the best
fit values for the 2 HOD parameters $\mu_1$ and $\mu_{1,p}$,
obtaining 13.05 and 0.79, respectively. The ratio of 
the original HSC precision matrix to the marginalized $N(z)$ 
one is  $1.15^{\nu_{\rm tot}}$, where $\nu_{\rm tot} = 94$ is the number of total
degrees of freedom of the system (i.e. size of the $C_\ell$
vector for all cross correlations between the tomographic bins).

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Tmat}
\caption{Visualization of the linear derivative matrix ${\sf T}
= {\partial \vt}/{\partial \vN}$ divided by the angular power
spectrum $C_{\ell}$ for all cross-correlation pairs between
the first tomographic bin and all four others.} 
\label{fig:Tmat}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Nzs}
\caption{Photometric redshift
distributions $N(z)$
of the four tomographic HSC bins.
The \textit{red} curves show the
default values used in the 
full HSC analysis \cite{1912.08209},
while the \textit{blue} curves 
show their smoothed and upsampled 
version used in this work. The
\textit{green} show a random 
Gaussian draw from the smoothing 
prior described in Section~\ref{sssec:theory.prior.smooth}.}
\label{fig:Nzs}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./Cls}
\caption{Galaxy power spectrum, $C_\ell^{gg}$, between the four
tomographic bins. The \textit{black} curves illustrate the HSC-measured
power spectrum and error bars, while the
\textit{red} curves show the $C_\ell$s
computed using the posterior mean values
of the 6 HOD parameters from the
full HSC analysis \cite{1912.08209}. In 
\textit{green}, we show the angular power
spectrum obtained by using the smoothed
$N(z)$ distributions (see Fig.~\ref{fig:Nzs}). The \textit{blue}
curves correspond to the exact
calculation of the $C_\ell$s using the
perturbed $N(z)$ values in
Fig.~\ref{fig:Nzs}, and the 
\textit{lightblue} dotted lines
show the power spectra derived via
Taylor expansion: $C_\ell' = C_\ell +
 {\sf T} \left(\vN' - {\vN} \right)$.}
\label{fig:Cls}
\end{figure}

@@

 \hline
 \hline
\end{tabular}
\end{center}
\caption{$\chi^2$ values with respect to the HSC data of the 
four curves shown in Fig.~\ref{fig:Cls} using the original 
covariance used in the HSC analysis and the marginalized
$N(z)$ covariance developed in this work.}
\label{tab:lin}
\end{table}

\subsection{Impact of N(z) uncertainties on final parameters}
In this section, we summarize the main results of this
paper, showing in particular the effect of marginalization
of the photometric uncertainties on the resulting constraints
of cosmological parameters of interest. In our particular
case, these are the 6 HOD parameters described in the model
in Section~\ref{ssec:hsc.theory}. The marginalized $N(z)$ 
covariance is computed
assuming a fiducial set of values for the HOD parameters
listed in the previous section.

To study the effect on the covariance matrix
of the marginalization procedure described in detail
in Section~\ref{ssec:theory.nz_new}, we visualize the original
correlation matrix and its difference with the
marginalized matrix in Fig.~\ref{fig:fid_marg_cov}. The
main difference with the original matrix is
a positive contribution to the off-diagonal entries
for redshift samples in close proximity. We set the free
parameters of our model to the following values: 
\begin{itemize}
    \item $A_{\rm smooth} = 1$, 
    \item $A_{\rm noise} = 4.$,
    \item $N_{\rm upsample} = 3$, 
    \item $\Delta z_{\rm thresh} = 0.06$.
\end{itemize}
These values were chosen so as to reduce the
$\chi^2$ of the perturbed model 
using the new covariance matrix when compared with the
original covariance matrix. The modest value of the
smoothing parameter, $A_{\rm smooth}$, ensures that we 
are not oversmoothing the $N(z)$ distribution, while
the choice of photometric noise as four times 
larger than the variance in the different photometric
measures provides a reasonable guess for the expected
variation in $N(z)$ given the uncertainty.

To assess whether the marginalization procedure 
proposed in this work provides better constraints
on the 6 HOD parameters than the original 14-parameter
model, we employ the MCMC ensemble sampler
$\textbf{emcee}$ \cite{2013PASP..125..306F}
setting the
 walkers' ratio to 6 and
 the number of iterations to 12000. We test
the convergence of the chains using a simple Gelman-Rubin convergence diagnostic
after analyzing the auto-correlation statistics and thinning the
chains appropriately. In all cases, we find that the
chains are reasonably well converged,
which gives more credibility to the 
conclusions we draw.

In Fig.~\ref{fig:fid_marg_cov} and Table~\ref{tab:chi2_fid},
we illustrate the key  comparison between the original HSC
covariance matrix and the marginalized
one developed in this paper. One can
notice that the full analysis (\textit{in gray}) leads to 
suboptimal constraints on the parameters
when compared with the marginalized
covariance (\textit{in blue}) in almost all cases
except for those HOD parameters which are poorly
constrained by the HSC dataset. 
Furthermore, the proximity
of the \textit{blue} and \textit{red} 
contours serves both as a sanity check 
that our method yields physical constraints
of the 6 parameters (i.e. not exceeding
the cosmic variance limits) while at the same time 
nearly optimal such (as 
our inferences are always limited
by cosmic variance).

To check the robustness of our result, we furthermore
run the following several tests:
\begin{itemize}
\item[\textbf{Test 1}:] We study the effect of the smoothing
by turning it off, $A_{\rm smooth} = 0$. 
\item[\textbf{Test 2}:] We vary the choice for the
diagonal photometric noise parameter
by increasing it ten-fold, $A_{\rm noise} = 42$.
\item[\textbf{Test 3}:] We compute the ${\sf T}$ matrix 
using a different set of 
HOD parameters perturbed by $1\sigma$
relative to the \textbf{fiducial} ones (listed in Section \ref{ssec:hsc.lin}).
\end{itemize}
We show the comparisons between
these three tests and the
fiducial marginalized $N(z)$ model in Fig.
\ref{fig:triangle_marg_tests} and Table~\ref{tab:chi2_tests}.
One can notice that the effect of the
smoothing on the constraints is negligible,
while increasing the diagonal noise
weakens them. Neither of these
tests changes significantly the
mean of the posterior distribution.
On the other hand, offsetting the 
HOD parameters used in the ${\sf T}$
matrix computation leads to a shift to
the mean and a slight widening of the
contours. That is because the covariance
matrix used in the analysis no longer
favors the HOD values preferred by the
data. This slight tension
results in sub-par convergence
of the chains and shifted mean posteriors.

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{./corr_diff}
\end{subfigure}
\caption{Correlation matrix of the original HSC dataset (\textit{left} panel) and difference between the
original and the marginalized (this work)
correlation matrices (\textit{right} panel). Most of the
effect of marginalizing for the shift and width
parameters is manifested as a positive contribution
to the original matrix near the diagonal (i.e. there
is an increase in correlation for close redshift
values). Note that we have subtracted the diagonal
off the two matrices.}
\label{fig:fid_marg_cov}
\end{figure}

@@

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{./triangle_marg_tests}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using different choices for the marginalized covariance matrix: in \textit{green}, we show the result where the diagonal noise is set to a very large value ($A_{\rm noise} = 42$); in \textit{gray} is shown the case where the marginalization is performed assuming fiducial HOD-model values which are $1\sigma$ away from their posterior mean values taken from Ref.~\cite{1912.08209}; in \textit{red}, we display the case where the smoothing has been removed ($A_{\rm smooth} = 0$); and finally the \textit{blue} contours show the fiducial case with $A_{\rm noise} = 4$ and $A_{\rm smooth} = 1$.}
\label{fig:triangle_marg_tests}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & HSC cov. [68\%, 95\%] & CV constraints [68\%, 95\%] & Marg. $N(z)$ [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 87.49/80 & --- & 88.54/88 \\ 
$\mu_{{\rm min},p}$ & $-0.5^{+1.7}_{-2.0}$, $^{+4.0}_{-4.0}$ & $-0.4^{+1.1}_{-1.4}$, $^{+2.5}_{-2.3}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ \\ [1ex]
$\mu_{\rm min}$ & $11.90^{+0.26}_{-0.15}$, $^{+0.39}_{-0.46}$ & $11.86^{+0.19}_{-0.16}$, $^{+0.28}_{-0.30}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ \\ [1ex]
$\mu_{0,p}$ & $2.4\pm 4.3$, $^{+7.2}_{-7.0}$ & $2.1^{+4.2}_{-5.1}$, $^{+6.6}_{-7.2}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.7\pm 3.3$, $^{+5.5}_{-5.5}$ & $6.1^{+4.6}_{-3.8}$, $^{+5.2}_{-4.8}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ \\ [1ex]
$\mu_{1,p}$ & $0.9^{+2.0}_{-2.8}$, $^{+5.1}_{-4.7}$ & $0.9^{+1.3}_{-1.8}$, $^{+3.4}_{-2.9}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ \\ [1ex]
$\mu_{1}$ & $13.10^{+0.30}_{-0.21}$, $^{+0.48}_{-0.54}$ & $13.04\pm 0.21$, $^{+0.38}_{-0.40}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\caption{Minimum $\chi^2$ values (divided by the degrees
of freedom) reached in each of the three MCMC runs
and [68\%, 95\%] constraints on the 6 HOD parameters
in the following scenarios: 1) adopting the original
HSC covariance matrix with 14 
parameters (6 HOD + 8 $N(z)$ ones), 2)
importance-sampling the original
chain to get cosmic variance constraints on 
the parameters, and 3) using the
marginalized $N(z)$ covariance matrix
developed in this work to constrain
the 6 HOD parameters.}
\label{tab:chi2_fid}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c | c c c c} 
 \hline\hline
 Parameter & Fiducial [68\%, 95\%] & Test 1 [68\%, 95\%] & Test 2 [68\%, 95\%] & Test 3 [68\%, 95\%] \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 88.54/88 & 87.67/88 & 88.56/88 & 78.61/88 \\ 
$\mu_{{\rm min},p}$ & $-0.3^{+1.5}_{-1.8}$, $^{+3.2}_{-2.8}$ & $0.0\pm 1.7$, $^{+3.2}_{-3.3}$ & $-0.3^{+1.4}_{-1.8}$, $^{+3.2}_{-2.8}$ & $-0.8^{+1.8}_{-2.1}$, $^{+3.7}_{-3.5}$ \\ [1ex]
$\mu_{\rm min}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.32}_{-0.36}$ & $11.85^{+0.22}_{-0.13}$, $^{+0.31}_{-0.37}$ & $11.83^{+0.21}_{-0.15}$, $^{+0.33}_{-0.36}$ & $11.76^{+0.26}_{-0.17}$, $^{+0.38}_{-0.43}$ \\ [1ex]
$\mu_{0,p}$ & $2.7^{+6.7}_{-4.4}$, $^{+6.9}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ & $2.5\pm 4.3$, $^{+7.1}_{-7.1}$ \\ [1ex]
$\mu_{0}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.8^{+3.6}_{-5.2}$, $^{+5.6}_{-5.5}$ & $5.8\pm 3.4$, $^{+5.5}_{-5.5}$ & $5.9\pm 3.4$, $^{+5.5}_{-5.6}$ \\ [1ex]
$\mu_{1,p}$ & $1.0^{+1.6}_{-2.6}$, $^{+4.1}_{-3.5}$ & $1.5^{+2.1}_{-2.6}$, $^{+4.3}_{-3.9}$ & $0.98^{+1.5}_{-2.5}$, $^{+4.2}_{-3.5}$ & $0.6^{+1.9}_{-2.9}$, $^{+4.6}_{-4.0}$ \\ [1ex]
$\mu_{1}$ & $13.00^{+0.25}_{-0.21}$, $^{+0.42}_{-0.44}$ & $13.03^{+0.26}_{-0.20}$, $^{+0.41}_{-0.45}$ & $13.00^{+0.25}_{-0.22}$, $^{+0.42}_{-0.44}$ & $12.93^{+0.29}_{-0.24}$, $^{+0.47}_{-0.50}$ \\ [1ex]
 \hline
 \hline
\end{tabular}
\end{center}
\caption{Minimum $\chi^2$ values (divided by the degrees
of freedom) attained in each of the four MCMC runs
and [68\%, 95\%] constraints on the 6 HOD parameters. The
``fiducial'' column displays the results for the marginalized
$N(z)$ covariance matrix adopting the fiducial parameter
choices described in the text, while the three tests
refer to the marginalized $N(z)$ covariance matrix
obtained with no smoothing, large diagonal noise and
$1\sigma$-offset HOD parameters, respectively.}
\label{tab:chi2_tests}
\end{table}
